Matching Bullets

### 2015-12-14 imaging-paper.Rnw
Rebuild the PDF

\subsection{Loess Fit}
In an approach to improve upon the previous algorithm, we first have to eliminate 
%To improve upon the previous algorithm, the first step must be to eliminate
the grooves from the images under the assumption that they do not contain relevant information for determining a match.
Fortunately, the location and appearance of the grooves in these 2d plots is quite consistent.
Surface measurements %beginning at $y = 0$ 
reach local maxima around the peak of the groove at either end of the range of $y$, we can then follow the descent of the surface measurements inwards to the valley of the groove. 
This marks the point at which we should trim the image. %We repeat a similar procedure for the right-hand groove by starting at the maximum y value and working backwards. 
The procedure can be described as follows:

>>>>

\subsection{Loess Fit}
In an approach to improve upon the previous algorithm, we first have to eliminate the grooves from the images under the assumption that they do not contain relevant information for determining a match.
Fortunately, the location and appearance of the grooves in these 2d plots is quite consistent.
Surface measurements reach local maxima around the peak of the groove at either end of the range of $y$, we can then follow the descent of the surface measurements inwards to the valley of the groove. 
This marks the point at which we should trim the image. The procedure can be described as follows:
